Type theories as quotient inductive-recursive types

### 2025-02-26 tex/main.tex
Remove the referral to function clauses

\usepackage[obeyFinal,textsize=footnotesize]{todonotes}
\usepackage{float}
\usepackage{manfnt}
\usepackage{mathpartir}
\newcommand{\danger}{\marginpar[\hfill\dbend]{\dbend\hfill}}
\newcommand{\LT}[2][]{\todo[inline,author={L-T},caption={},color={pink},#1]{#2}}
\newcommand{\Gene}[2][]{\todo[inline,author={Gene},caption={},#1]{#2}}
\newcommand{\Fredrik}[2][]{\todo[inline,author={Fred},caption={},#1]{#2}}
\lstset{
    breaklines=true,
    breakatwhitespace=true,
    literate=%
      {≡}{$\equiv$}1
      {Γ}{$\Gamma$}1
      {Δ}{$\Delta$}1 
      {→}{$\to$}1
      {≅}{$\cong$}1
}

@@

\subparagraph*{Implementing overlapping patterns via rewrite rules}
%The mechanism of defining a function by overlapping patterns is only implemented in an outdated experimental fork of \Agda.
To emulate a function by overlapping patterns, we declare each function clause a rewrite, together with another rewrite to identify the witness as the reflexivity proof $\mathsf{refl}$.
For example, the first few clauses for type substitution (written $[\sigma]_{\Ty}\,A$ rather than $\subTy{A}{\sigma}$ in the formalisation) are defined as
\begin{lstlisting}
postulate
  [_]_      : Sub Γ Δ → Ty Δ → Ty Γ
  [id]      : [ idS ]    A ≡ A
  {-# REWRITE [id]      #-}
  [id]≡refl : [id] {A = A} ≡ refl
  {-# REWRITE [id]=refl #-}
\end{lstlisting}
where \lstinline|[id]≡refl| ensures that \lstinline|[id]| disappears in transports.
We also turn on the option \texttt{-{}-local-confluence-check}  to check local confluence.
%
Overlapping patterns is indeed one of the use cases of user-defined rewrite rules discussed by Cockx~\cite{Cockx2020}.
The caveat, though, is that the termination checking is not imposed, so we need to check termination informally.

>>>>

\usepackage[obeyFinal,textsize=footnotesize]{todonotes}
\usepackage{float}
\usepackage{manfnt}
\usepackage{mathpartir}
\newcommand{\danger}{\marginpar[\hfill\dbend]{\dbend\hfill}}
\newcommand{\LT}[2][]{\todo[inline,author={L-T},caption={},color={pink},#1]{#2}}
\newcommand{\Gene}[2][]{\todo[inline,author={Gene},caption={},#1]{#2}}
\newcommand{\Fredrik}[2][]{\todo[inline,author={Fred},caption={},#1]{#2}}
\lstset{
    breaklines=true,
    breakatwhitespace=true,
    literate=%
      {≡}{$\equiv$}1
      {Γ}{$\Gamma$}1
      {Δ}{$\Delta$}1 
      {→}{$\to$}1
      {≅}{$\cong$}1
      {σ}{$\sigma$}1
}

@@

\subparagraph*{Implementing overlapping patterns via rewrite rules}
%The mechanism of defining a function by overlapping patterns is only implemented in an outdated experimental fork of \Agda.
To emulate a function by overlapping patterns, we declare each function clause a rewriting rule and turn on the option \texttt{-{}-local-confluence-check}  to check local confluence.
For example, the first few clauses for type substitution (written $[\sigma]_{\Ty}\,A$ rather than $\subTy{A}{\sigma}$ in the formalisation) are defined as
\begin{lstlisting}
postulate
  [_]_ : Sub Γ Δ → Ty Δ → Ty Γ
  [id] : [ idS ] A ≡ A
  []U  : [ σ ]   U ≡ U
  {-# REWRITE [id] []U #-}
\end{lstlisting}
where \lstinline|A| and $\sigma$ are declared as genearlised variables.
%
Overlapping patterns is indeed one of the use cases of user-defined rewrite rules discussed by Cockx~\cite{Cockx2020}.
The caveat, though, is that the termination checking is not imposed, so we need to check termination informally.
